%!TEX root = ../thesis.tex
% створюємо список використаної літератури
\begin{thebibliography}    
    \bibitem{Chaffey}
    Chaffey D. Digital marketing: strategy, implemenation and practice / Dave Chaffey, Ellis-Chadwick Fiona. --- 6th ed. --- [S. l.] : Pearson, 2016. --- 702 p.
    
    \bibitem{Daniels}
    Daniels D. Email Marketing: An Hour a Day / David Daniels, Jeanniey Mullen. Indianapolis : Wiley Publishing, 2009. --- 291 p.
    
    \bibitem{Comrack}
    Comrack G. V. Email Spam Filtering A Systematic Review / Gordon V. Comrack. --- Hanover : Now Publishers, 2008. --- 136 p.
    
    \bibitem{manage}
    Manage domains --- Postmaster tools [Electronic resource] // Google Postmaster tools. --- Mode of access: \url{https://postmaster.google.com} (date of access: 29.04.2024). --- Title from screen.
    
    \bibitem{Wolford}
    Wolford B. How does the GDPR affect email? [Electronic resource] / Ben Wolford // GDPR.EU. --- Mode of access: \url{https://gdpr.eu/email-encryption/} (date of access: 28.04.2024). --- Title from screen.
    
    \bibitem{privacy}
    Privacy and Identity Management [Electronic resource] / ed. by M. Friedewald, S. Schiffner, S. Krenn. --- Cham : Springer International Publishing, 2021. --- Mode of access: \url{https://doi.org/10.1007/978-3-030-72465-8} (date of access: 28.04.2024). --- Title from screen.
    
    \bibitem{turn}
    Turn Emails into Revenue [Electronic resource] // Intuit Mailchimp. --- Mode of access: \url{https://mailchimp.com} (date of access: 11.05.2024). --- Title from screen.

 
\end{thebibliography}
